\documentclass{letter}
\signature{Joseph Mifsud}
\address{5 Spencer Way \\ Robbinsville, NJ 08691 \\ United States of America}
\begin{document}
\begin{letter}{Corvus Insurance\\ 100 Summer St.\\ Boston, MA 02110\\ United States of America}
\opening{Greetings,}
I am excited to apply for the role of Data Analyst at Corvus Insurance because of the gameplay of Corvus.
Corvids' robust playstyle features some of the best abilities granted by investment in the intelligence skill-tree.
The curiosity ability allows corvidae to investigate situations from different vantage points, encouraging profitable outcomes.
Further, corvids implement a fierce social game. 
When useful, corvids may create elaborate distractions to give teammates the opportunity to steal the resources of opposing factions like the canidae.
Their curiosity, use of tools, and social-play make them a top-tier competitor in the current meta on 5 different continents.

Any competitor in the global food-chain who isn't hungry to compete faces extiction.
As the environment changes, and presents new challenges, hunger-motivated curiosity has allowed the corvids to flourish.
My hunger motivates me to adapt to the circumstance of the hour.
Many jobs that exist Today did not when I first considered career during high school.
A lot has changed since 2007, but not my play-style.
I leverage my curiosity to adjust my skill set for a better vantage on the target.
I am able to motivate myself to accomplish great things, to be bold, and to bring an all iron endurance to life's misfortunes.

As a open-source software contributor and a freelance data scientist I have a history accomplishments.
Most recently, I completed a project which clustered neighborhoods in Brooklyn to identify optimal locations to open a small business.
Four locations were recommended to a position within 600 meters.

My ability to work independently or as a member of a team gives Envision great flexibility on assignment.
No only that, my experience in education allows me to speak both colloquially or with technical precision.
This allows for meaningful engagement with the wide variety of professionals with which Corvus engages.

Finally, I believe in making data-driven, goal-oriented, decision making which has led me right here to engage with you. 
\closing{Happy Hunting,}
\encl{Resume}
\end{letter}
\end{document}

